---
title: "ValencePlots"
author: "lushi"
date: "26/01/2019"
output: html_document
---

```{r setup, include=FALSE}
library(ggplot2)
library(gridExtra)
library(stringr)
```

## Valence plot 

* This script generates valence plot in T1, T2, T3
* here we have time series plot with CESD timeline and time series plot with calendar date time line
* for time series plot with CESD timeline, we adjusted day valence by deducting valence with calendar date mean valence 



```{r read file}
file<- read.csv('~/phd_work/depression dessertation/data/sub_3year.csv')
cesd<- read.csv('~/phd_work/depression dessertation/data/depression_fix_nohis.csv')
```

Plot cesd time series, the day before they fill out cesd scale as day 1
```{r}
file2 <- file

#average sentiment in each actual day
senti_actual <- aggregate(sentiment ~ time, file2, sum)
count_senti_actual <- aggregate(userid ~ time, file2, length)
#average sentiment 
aver_senti_actual <- merge(senti_actual, count_senti_actual, by='time')
aver_senti_actual$aver_senti <- aver_senti_actual$sentiment/aver_senti_actual$userid
aver_senti_actual <- aver_senti_actual[,c('time','aver_senti')]

#actual mean valence is 0.09717126 per day
mean(aver_senti_actual$aver_senti)

#normalise user sentiment by actual average day sentiment in the entire sample, sentiment x, sample average
file3 <- merge(aver_senti_actual, file2, by ='time')
file3$sentiment_timeS <- file3$sentiment - file3$aver_senti

#valence before normalise
mean(file3$sentiment)
#0.09758262

#valence after normalise, close to the mean
mean(file3$sentiment_timeS)
#1.625813e-19

#aggregate by date
count_senti <- aggregate(sentiment_timeS ~ day, file3, sum)
count_len <- aggregate(userid ~ day, file3, length)
count  <- merge(count_senti, count_len, by = 'day')

#average sentiment of user in the timeseries
count$ave_senti_ts <-  count$sentiment_timeS/count$userid
  
# ggplot(data=count, aes(x=day)) + 
#   stat_smooth(aes(y = ave_senti_ts), method = "lm",
#               formula = y ~ poly(x, 3), se = FALSE) +
#   ggtitle("Post sentiment in 3 years") +
#   xlab("Day") + ylab("Post sentiment")

```

Here we set the cesd cut off point
```{r define cesd cut off point}
#cesd sum
cesd$cesd_sum <- rowSums(cesd[,3:13])
all <- merge(file3,cesd, by = 'userid')

high <- all[all$cesd_sum > 35, ]
low <- all[all$cesd_sum <= 16, ]
```

valence plot
```{r}
#We plot both group together because both group have 1095 days with sentiment data available
#Lgroup sentiment
#aggregate by date  #1095 days
count_sentiH <- aggregate(sentiment_timeS ~ day, high, sum)
count_lenH <- aggregate(userid ~ day, high, length)
countH  <- merge(count_sentiH, count_lenH, by = 'day')

#average sentiment of used in the timeseries, sentiment score divided by number of posts
countH$ave_senti_ts <-  countH$sentiment_timeS/countH$userid

#Lgroup sentiment
#aggregate by date #1095 days
count_sentiL <- aggregate(sentiment_timeS ~ day, low, sum)
count_lenL <- aggregate(userid ~ day, low, length)
countL  <- merge(count_sentiL, count_lenL, by = 'day')

#average sentiment  in the timeseries 
countL$ave_senti_ts <-  countL$sentiment_timeS/countL$userid
countL2 <- countL[,c('day','ave_senti_ts')]
colnames(countL2) <- c('day', 'lowS')

#merge high and low group
myplot1 <- function(plotdata,title) {
  p <- ggplot(data=plotdata, aes(x=day)) + 
    stat_smooth(aes(y = ave_senti_ts), method = "lm",
                formula = y ~ poly(x, 3), se = FALSE, color = 'red') +
    stat_smooth(aes(y = lowS), method = "lm",
                formula = y ~ poly(x, 3), se = FALSE) +
    ggtitle(title) +
    xlab("Day") + ylab("Post sentiment")
  return (p)
}

plotdata <- merge(countL2, countH, by='day')
p1 <- myplot1(plotdata,"Post sentiment in 3 years")

#select 1 year data
oneYear <- plotdata[plotdata$day <= 365, ]
p2 <- myplot1(oneYear, "Post sentiment in 1 year")

#select 1 month data
oneM <- plotdata[plotdata$day <= 30, ]
p3<- myplot1(oneM, "Post sentiment in 1 year")
grid.arrange(p1, p2, p3, nrow = 1)
```
valence t test in T1 (3 year), T2(1 year), T3(1 month) (for table 1)
```{r}
library(lsr)
t.test(plotdata$lowS,plotdata$ave_senti_ts)
cohensD(plotdata$lowS,plotdata$ave_senti_ts)

t.test(oneYear$lowS,oneYear$ave_senti_ts)
cohensD(oneYear$lowS,oneYear$ave_senti_ts)

t.test(oneM$lowS,oneM$ave_senti_ts)
cohensD(oneM$lowS,oneM$ave_senti_ts)
```





Valence plot, postive and negative valence
p1 Negative sentiment in 3 years, P2 Negative sentiment in 1 year, P3 Negative sentiment in 30 days
p3 Positive sentiment in 3 years, P4 Positive sentiment in 1 year, P5 Positive sentiment in 30 days
```{r}
#here we can't plot both group together because the H group has 243 days, L group has 216 days in one year, 
#these days are likely not over lap, but we can adjust the y axis so that both graphs are on the same scale
#the valence is normalized with actual valence each day


#this function compute negative/positive sentiment in 3 years
#this function aggregate the sentiment of posts and divide sentiment sum with number of posts
getSenti <- function(mydata) {
  NV_h2 <- aggregate(sentiment_timeS ~ day, mydata, sum)
  count_NV_h <- aggregate(userid ~ day, mydata, length)
  count_NV_h2  <- merge(NV_h2, count_NV_h, by = 'day')
  
  #average sentiment of used in the timeseries, sentiment score divided by number of posts
  count_NV_h2$cesd_g <-  count_NV_h2$sentiment_timeS/count_NV_h2$userid
  count_NV_h2 <- count_NV_h2[ ,c('day','cesd_g')]
  
  return (count_NV_h2)
}

#high group 
NV_h <- high[high$sentiment_timeS < 0, ]
count_NV_h2 <- getSenti(NV_h)
#low group
NV_l <- low[low$sentiment_timeS < 0, ]
count_NV_l2 <- getSenti(NV_l)

#plot negative valence cesd_g.x: high  cesd_g.y: low
myplot <- function(mydata,title) {
  p <- ggplot(data=mydata, aes(x=day)) + 
    stat_smooth(aes(y = cesd_g.x), method = "lm",
                formula = y ~ poly(x, 3), se = FALSE, color = 'red') +
    stat_smooth(aes(y = cesd_g.y), method = "lm",
                formula = y ~ poly(x, 3), se = FALSE, color = 'blue') +

    # geom_point(aes(y = cesd_g.x, colour="low", size=2))+
    # geom_point(aes(y = cesd_g.y, colour="high", size=2))+
    ggtitle(title) +
    xlab("Day") + ylab("Post sentiment")+
    theme(text = element_text(size=20), axis.text.x = element_text(size= 20, angle=0, hjust=1),
          axis.text.y = element_text(size= 20, angle=0, hjust=1),
          axis.title.y = element_text(size= 25, angle=90),
          axis.title.x = element_text(size= 25, angle=0))
  
  return (p)
}


#merge high and low group
NV <- merge(count_NV_h2, count_NV_l2, by = 'day')
p1 <- myplot(NV, "Negative valence in 3 Yrs")

oneY_NV <- NV[NV$day <= 365, ]
p2 <- myplot(oneY_NV, "Negative valence in 1 Yr")

oneM_NV <- NV[NV$day <= 30, ]
p3 <- myplot(oneM_NV, "Negative valence in 30 D")



#plot positive valence
#high group 
PV_h <- high[high$sentiment_timeS >= 0, ]
count_PV_h2 <- getSenti(PV_h)
#low group
PV_l <- low[low$sentiment_timeS >=  0, ]
count_PV_l2 <- getSenti(PV_l)


PV <- merge(count_PV_h2, count_PV_l2, by = 'day')
p4 <- myplot(PV, "Positive valence in 3 Yrs")

oneY_PV <- PV[PV$day <= 365, ]
p5 <- myplot(oneY_PV, "Positive valence in 1 Yr")

oneM_PV <- PV[PV$day <= 30, ]
p6 <- myplot(oneM_PV, "Positive valence in 30 D")
grid.arrange(p1, p2, p3, p4, p5, p6 , nrow = 2)




```

## valence plot with calendar date timeline
P1 Sentiment in 3 years, P2 Negetive sentiment in 3 years, P3 Positive sentiment in 3 years
change CESD score to get polarized groups

```{r pressure, echo=FALSE}
####plot sentiment in actual date

aver_senti_actual$time2 <- as.Date(aver_senti_actual$time)

h1 <- high[,c('time','sentiment')]
l1 <- low[,c('time','sentiment')]

getData2 <- function(h1,l1) {
  h <- aggregate(sentiment ~ time, data = h1, sum)
  count <- aggregate(sentiment ~ time, data = h1, length)
  h$sentiment1 <- h$sentiment/count$sentiment
  
  l <- aggregate(sentiment ~ time, data = l1, sum)
  count <- aggregate(sentiment ~ time, data = l1, length)
  l$sentiment1 <- l$sentiment/count$sentiment
  
  h <- h[, c('time', 'sentiment1')]
  colnames(h) <- c('time','high')
  l <- l[, c('time', 'sentiment1')]
  
  m <- merge(h,l, by = 'time')
  m$time <- as.Date(m$time)
  return (m)
}


myPlot5 <- function(mydata,title) {

  p<- ggplot(data=mydata, aes(x=time))+ 
    stat_smooth(aes(y = high), method = "lm",
                formula = y ~ poly(x, 3), se = FALSE, color = 'red') +
    stat_smooth(aes(y = sentiment1), method = "lm",
                formula = y ~ poly(x, 3), se = FALSE) +
    ggtitle(title) +
    xlab("Day") + ylab("Post sentiment")+
    theme(text = element_text(size=20), axis.text.x = element_text(size= 20, angle=0, hjust=1),
          axis.text.y = element_text(size= 20, angle=90, hjust=1),
          axis.title.y = element_text(size= 25, angle=90),
          axis.title.x = element_text(size= 25, angle=0))
  
  return (p)
}

Nh <- h1[h1$sentiment < 0, ]
Nl <- l1[l1$sentiment < 0, ]
mN <- getData2(Nh,Nl)
Ph <- h1[h1$sentiment >= 0, ]
Pl <- l1[l1$sentiment >= 0, ]
mP <- getData2(Ph,Pl)
m <- getData2(h1,l1)


p1 <- myPlot5(m, "Valence in 3 years")
p2 <- myPlot5(mN, "Negetive valence in 3 years")
p3 <- myPlot5(mP, "Positive valence in 3 years")


grid.arrange(p1, p2, p3, nrow = 1)


```


